---
title: "Kiplinger23"
author: "Lucia Walinchus"
date: "2023-09-19"
output: html_document
---

```{r setup, include=FALSE}
library(dplyr)
library(tidyverse)
library(lubridate)
library(ggplot2)
library(gganimate)
library(gapminder)
library(gifski)
```

## Filtering for our countries

Our fellows today come from: 
Croatia - Dr. Kristian Dosen, investigative reporter and a professor at University of Zagreb
Czech Republic - Filip Rozanek, editor of Digizonecz
India - Joseph Kootungal Jose, radio host for Entertainment Network Limited
Pakistan - Naeem Akbar Sahoutara, reporter, Dawn
Palestine - Haneen Baker, Head of English Department, An-Najah National University
Nigeria - Aniekeme Finbarr Uklong, special assistant to the governor, Akwa Ibom State
Vietnam - Tien Ahn Tuan Nguyen, head of visual desk, Dan Tri newspaper
Lithuania - Martynas Vainutis, editor, UAB Kasko Group

```{r}
gapminder_filtered <- gapminder %>% 
  filter(country=="Croatia"|
         country=="Czech Republic"|
         country=="India"|
         country=="Pakistan"|
         country=="Palestine"|
         country=="Nigeria"|
         country=="Vietnam"|
         country=="Lithuania")
```

Summary of our data: 

```{r}
summary(gapminder_filtered)
```
#Simple chart: Population

```{r}
gapminder_filtered %>% 
  filter(year==2007) %>% 
ggplot( aes(x=country, y=pop, fill=country))+
         geom_col()+
  labs(title = "Population of Select Countries (2007)")
```






## Animated

```{r}

ggplot(gapminder_filtered, aes(gdpPercap, lifeExp, size = pop, colour = country)) +
  geom_point(alpha = 0.7, show.legend = TRUE) +
  scale_colour_manual(values = country_colors) +
  scale_size(range = c(2, 12)) +
  scale_x_log10() +
  labs(title = 'Year: {frame_time}', x = 'GDP per capita', y = 'life expectancy') +
  transition_time(year) +
  ease_aes('linear')
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
